Estimate Non-zero mode

### 2017-01-15 analysis/adaptive_shrinkage.Rmd
Split setting chunk options and loading packages into separate chunks; re-rendered adaptive_shrinkage.Rmd, ash_npmle.Rmd, checkIP.Rmd, check_mixfdr_lownoise.Rmd, efron.fcr.Rmd, estimate_mode.Rmd and template.Rmd.

First, we load the necessary libraries, and specify settings for
displaying the plots in the rendered document.

```{r chunk_options, include=FALSE}
library(REBayes)
library(ashr)
library(ggplot2)
library(scales)
source("chunk-options.R")
```

>>>>

First, we load the necessary libraries.

```{r packages}
library(REBayes)
library(ashr)
library(ggplot2)
library(scales)
```

```{r chunk_options, include=FALSE}
# Specify settings for displaying the plots in the rendered document.
source("chunk-options.R")
```

### 2017-01-15 analysis/ash_npmle.Rmd
Split setting chunk options and loading packages into separate chunks; re-rendered adaptive_shrinkage.Rmd, ash_npmle.Rmd, checkIP.Rmd, check_mixfdr_lownoise.Rmd, efron.fcr.Rmd, estimate_mode.Rmd and template.Rmd.

First, we load the necessary libraries, and specify settings for
displaying the plots in the rendered document.

```{r chunk_options, include=FALSE}
library(REBayes)
library(ashr)
source("chunk-options.R")
```

>>>>

First, we load the necessary libraries.

```{r packages}
library(REBayes)
library(ashr)
```

```{r chunk_options, include=FALSE}
# Specify settings for displaying the plots in the rendered document.
source("chunk-options.R")
```

### 2017-01-15 analysis/checkIP.Rmd
Split setting chunk options and loading packages into separate chunks; re-rendered adaptive_shrinkage.Rmd, ash_npmle.Rmd, checkIP.Rmd, check_mixfdr_lownoise.Rmd, efron.fcr.Rmd, estimate_mode.Rmd and template.Rmd.

First, we load the necessary libraries, and specify settings for
displaying the plots in the rendered document.

```{r chunk_options, include=FALSE}
library(ggplot2)
library(dplyr)
library(reshape2)
source("chunk-options.R")
```

>>>>

First, we load the necessary libraries.

```{r packages}
library(ggplot2)
library(dplyr)
library(reshape2)
```

```{r chunk_options, include=FALSE}
# Specify settings for displaying the plots in the rendered document.
source("chunk-options.R")
```

### 2017-01-15 analysis/efron.fcr.Rmd
Split setting chunk options and loading packages into separate chunks; re-rendered adaptive_shrinkage.Rmd, ash_npmle.Rmd, checkIP.Rmd, check_mixfdr_lownoise.Rmd, efron.fcr.Rmd, estimate_mode.Rmd and template.Rmd.

First, we load the necessary libraries, and specify settings for
displaying the plots in the rendered document.

```{r chunk_options, include=FALSE}
library(ashr)
library(qvalue)
library(locfdr)
source("chunk-options.R")
```

>>>>

First, we load the necessary libraries.

```{r packages}
library(ashr)
library(qvalue)
library(locfdr)
```

```{r chunk_options, include=FALSE}
# Specify settings for displaying the plots in the rendered document.
source("chunk-options.R")
```

### 2017-01-15 analysis/estimate_mode.Rmd
Rendered referee_uaza.html and fixed chunk-options label to chunk_options.
Split setting chunk options and loading packages into separate chunks; re-rendered adaptive_shrinkage.Rmd, ash_npmle.Rmd, checkIP.Rmd, check_mixfdr_lownoise.Rmd, efron.fcr.Rmd, estimate_mode.Rmd and template.Rmd.

First, we load the necessary libraries, and specify settings for
displaying the plots in the rendered document.

```{r chunk-options, include=FALSE}
library(ashr)
source("chunk-options.R")
```

>>>>

First, we load the necessary libraries.

```{r packages}
library(ashr)
```

```{r chunk_options, include=FALSE}
# Specify settings for displaying the plots in the rendered document.
source("chunk-options.R")
```
